Computer Vision-based System for Impaired Human Vision Compensation

### 2018-09-23 article.tex
Some changes to the content, mostly Introduction. I made several comments on Results and Discussion. Please take a look at them

According to \cite{Bourne} more than $250$ million persons have moderate to severe vision impairment ($\approx 36$ million are blind). During past decades significant effort was devoted by various authors to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the world around. However, computer vision is rapidly evolving field, and systems based on aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe realistic system, which allow to use modern computer vision methods for compensation of lost or impaired vision function in humans. The article is organized as follows: in Section~\ref{sec:method} we describe our method, Section~\ref{sec:results} contains schematic and description of human vision compensation system (HVCS), which is the result of this research, and Section~\ref{sec:discussion} is devoted for the discussion.

@@

%\newpage
%patarciau skyreli vadint "Results" o ne "System".
\section{Results}
\label{sec:results}

@@

Following the above methodology we suggest impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).

\textbf{Device} subsystem is continuously carried by the user. It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to carry out required computations or forward them to external server via Internet connection. Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU. Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user. %We suggest to use bone conductive headphones, ...

@@

\section{Discussion}
\label{sec:discussion}

In this article we outlined an idea of computer vision-based sensor, which can help to partially compensate impaired or lost human sight. The developed head mounted tactile device is deveolped for head position and orientation tracking and could capture an image in front of visually impaired people. The tactile device with integrated 3D deph camera is integrated with smartphone by bluetooth which could preprocess the labeled image features. The developed high quality self navigation system is based on the computer vision methods especially enhancing the capabilities to detect and classify objects (e.g bus station, street crossings, ) with their surrounding objects. The authors expect to increase the capabilies of potentially blind to secure navigate especially for the planed destination (e.g. "home-office").

@@

>>>>

More than $250$ million poople worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world. However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previuosly proposed electronic aids for the blind count on highly specialised hardware, for instance smart glassess \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photosensors and cameras \cite{Larisa}. Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of the white cane. This project puts major emphasis on developing a tool, which seamlesly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone). This paper describes the high level architecture of the proposed technology aid for visually impaired people.

%The article is organized as follows: in Section~\ref{sec:method} we describe our method, Section~\ref{sec:results} presents the schematic description of human vision compensation system (HVCS). Limitations and further implications of the proposed system are discussed in the Section~\ref{sec:discussion}.

@@

\section{Results}
\label{sec:results}

@@

Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).

%padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
% tai kas dabar yra prie Inference, siulau perprazuot kaip Functionality, ka as minejau Method. Taip pat visa Results skyreli reiktu labiau susiet su Method. Reiktu, kad visi 4 Method pamineti punktai isrysketu ir Results. 
%Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.
\textbf{Device} subsystem is a computational device the user currently uses for completing other daily tasks. It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via Internet connection. Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU. Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user. %We suggest to use bone conductive headphones, ...

@@

\section{Discussion}
\label{sec:discussion}
%Didzioji Discussion teksto dalis man labiau tinka prie Results/Conclusion. Gal galim padiskutioti daugiau apie Limitations, Future Implications, Lessons Learned ar pan... Cia galime savo siuloma sistema lyginti su anksciau publikuotais rezultatais.

In this article we outlined an idea of computer vision-based sensor, which can help to partially compensate impaired or lost human sight. The developed head-mounted tactile device is developed for head position and orientation tracking and could capture an image in front of visually impaired people. The tactile device with integrated 3D deph camera is integrated with smartphone by bluetooth which could preprocess the labeled image features. The developed high quality self navigation system is based on the computer vision methods especially enhancing the capabilities to detect and classify objects (e.g bus station, street crossings, ) with their surrounding objects. The authors expect to increase the capabilies of potentially blind to secure navigate especially for the planed destination (e.g. "home-office").

@@

\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M. Smart Assistive Navigation System for Blind and Visually Impaired Individuals. 2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.

\bibitem{Larisa} Dunai, L. D., Lengua, I. L., Tortajada, I., Brusola Simon, F. Obstacle detectors for visually impaired people. 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM), 2014.
